Type Refinements for the Working Class

### 2016-01-03 paper.tex
Fix error in definition of approx

Now, we can extend $R_\tau$ to a new relation $[R_\tau]$ on closed expressions
which respects a single ``layer'' of computation. We will say
$\PBinRel{[R_\tau]}{\Upsilon}{M}{N}$ when, supposing
$\Eval{\Upsilon}{\tau}{M}{\App{\vartheta}{\Vec{E}}}$ such that
$\IsCanOperator{\Upsilon}{\vartheta}{\MkArity{\vec{v}}{\tau}}$,
for any
\begin{tikzcd}[cramped]
  \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
\end{tikzcd}
, we have $\Eval{\Upsilon'}{\tau}{\Rename{\rho}{N}}{\App{\Rename{\rho}{\vartheta}}{\Rename{\rho}{\Vec{F}}}}$ and
$\PBinRel{R_{\vec{v}}}{\Upsilon'}{\Rename{\rho}{\vec{E}}}{\Rename{\rho}{\vec{F}}}$.

>>>>

Now, we can extend $R_\tau$ to a new relation $[R_\tau]$ on closed expressions
which respects a single ``layer'' of computation. We will say
$\PBinRel{[R_\tau]}{\Upsilon}{M}{N}$ when, for any
\begin{tikzcd}[cramped]
  \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
\end{tikzcd}%
, supposing
$\Eval{\Upsilon'}{\tau}{\Rename{\rho}{M}}{\App{\vartheta}{\Vec{E}}}$ such that
$\IsCanOperator{\Upsilon'}{\vartheta}{\MkArity{\vec{v}}{\tau}}$,
we have $\Eval{\Upsilon'}{\tau}{\Rename{\rho}{N}}{\App{\vartheta}{\Vec{F}}}$ and
$\PBinRel{R_{\vec{v}}}{\Upsilon'}{\vec{E}}{\vec{F}}$.
